Constant Partying: \\ Introducing a Generic Toolkit for Recursive Partitioning in R

### 2014-03-18 pkg/partykit/inst/NUS-2014/constparty.Rnw
forgot one info slot in M&S tree
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@498 255f4249-2263-4417-b1ea-8498779e27a7

ms63p <- partynode(1L,
  split = partysplit(2L, index = 1:2),
  kids = list(
    partynode(2L,
      split = partysplit(3L, breaks = 65, right = FALSE),
      kids = list(
        partynode(3L,
	  split = partysplit(4L, index = 1:2),
	  kids = list(
	    partynode(4L,
	      split = partysplit(5L, breaks = 3L, right = FALSE),
	      kids = list(
	        partynode(5L,
		  split = partysplit(5L, breaks = 2L, right = FALSE),
		  kids = list(
		    partynode(6L, info = "$5000"),
		    partynode(7L, info = "$6500")
		  )
		),
		partynode(8L,
		  split = partysplit(3L, breaks = 45, right = FALSE),
		  kids = list(
		    partynode(9L, info = "$7000"),
		    partynode(10L, info = "$9000")
		  )
		)
	      )
	    ),
	    partynode(11L, info = "$4500")
	  )
	),
	partynode(12L,
	  split = partysplit(5L, breaks = 2L, right = FALSE),
	  kids = list(
	    partynode(13L, info = "$2200"),
	    partynode(14L, info = "$4500")
	  )
	)
      ),
      info = "$5500"
    ),
    partynode(15L,
      split = partysplit(5L, breaks = 2L, right = FALSE),
      kids = list(
        partynode(16L, info = "$2500"),
	partynode(17L, info = "$5000")
      )
    )
  ),
  info = "$5000"
)
ms63p <- party(ms63p, ms63d)
@

>>>>

ms63p <- partynode(1L,
  split = partysplit(2L, index = 1:2),
  kids = list(
    partynode(2L,
      split = partysplit(3L, breaks = 65, right = FALSE),
      kids = list(
        partynode(3L,
	  split = partysplit(4L, index = 1:2),
	  kids = list(
	    partynode(4L,
	      split = partysplit(5L, breaks = 3L, right = FALSE),
	      kids = list(
	        partynode(5L,
		  split = partysplit(5L, breaks = 2L, right = FALSE),
		  kids = list(
		    partynode(6L, info = "$5000"),
		    partynode(7L, info = "$6500")
		  )
		),
		partynode(8L,
		  split = partysplit(3L, breaks = 45, right = FALSE),
		  kids = list(
		    partynode(9L, info = "$7000"),
		    partynode(10L, info = "$9000")
		  )
		)
	      )
	    ),
	    partynode(11L, info = "$4500")
	  )
	),
	partynode(12L,
	  split = partysplit(5L, breaks = 2L, right = FALSE),
	  kids = list(
	    partynode(13L, info = "$2200"),
	    partynode(14L, info = "$4500")
	  )
	)
      ),
      info = "$5500"
    ),
    partynode(15L,
      split = partysplit(5L, breaks = 2L, right = FALSE),
      kids = list(
        partynode(16L, info = "$2500"),
	partynode(17L, info = "$5000")
      ),
      info = "$3000"
    )
  ),
  info = "$5000"
)
ms63p <- party(ms63p, ms63d)
@
